---
title: "Practice"
author: "Wenru Zhou"
date: "9/13/2018"
output:
  html_document: default
  pdf_document: default
---


 
```{r,results='hide',echo=FALSE,message=FALSE,warning=FALSE}
options(scipen=999)

library(Hmisc)
library(knitr)
library(devtools)
library(Table1)

source('Practice.R')
source('Macro.R')


#install_github("palmercl/Table1")

```

## Project 1
## Longitudinal assessment of the effect of hard drug use on the effect of HARRT in a multicenter AIDS cohort study

# Data introduction
This data is from a prospective cohort study with 3935 observations and 34 variables. Participants recevied HARRT treatment for HIV and were measured annually. They were scheduled for 9 visits from year-0 visit to year-8 visit. Year-0 visit is their last visit without HARRT treatment. Year-1 visit is the baseline. The missing status of data is listed.

Hard drug missing at baseline is `r missing_hard_drugs_count` (`r missing_hard_drugs_rate`).

**Table 0. Missing
***Baseline and three years after
```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
kable(con_missing, align=c('l','c','c'))

```


**Table 1. Demographic characteristics
***Baseline and three years after
```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
kable(con_final, align=c('l','c','c'))
```
